Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-04-28 publication/manuscript.Rmd
add orcid id

---
title: Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features
titlerunning: Encoding high cardinality features in supervised ML
authors:
  - name: Florian Pargent \orcidlink{0000-0002-2388-553X}
    email: florian.pargent@psy.lmu.de
    address: Department of Psychology, Psychological Methods and Assessment, LMU Munich, Leopoldstraße 13, 80802 Munich, Germany
    footnote: 1
  - name: Florian Pfisterer
    address: Department of Statistics, Statistical Learning and Data Science, LMU Munich, Ludwigstraße 33, 80539 Munich, Germany
  - name: Janek Thomas \orcidlink{0000-0003-4511-6245}
    address: Fraunhofer Institute for Integrated Circuits, Hansastraße 32, 8068 Munich, Germany
  - name: Bernd Bischl \orcidlink{0000-0001-6002-6980}
    address: Department of Statistics, Statistical Learning and Data Science, LMU Munich, Ludwigstraße 33, 80539 Munich, Germany

>>>>

---
title: Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features
titlerunning: Encoding high cardinality features in supervised ML
authors:
  - name: Florian Pargent \orcidlink{0000-0002-2388-553X}
    email: florian.pargent@psy.lmu.de
    address: Department of Psychology, Psychological Methods and Assessment, LMU Munich, Leopoldstraße 13, 80802 Munich, Germany
    footnote: 1
  - name: Florian Pfisterer \orcidlink{0000-0001-8867-762X}
    address: Department of Statistics, Statistical Learning and Data Science, LMU Munich, Ludwigstraße 33, 80539 Munich, Germany
  - name: Janek Thomas \orcidlink{0000-0003-4511-6245}
    address: Fraunhofer Institute for Integrated Circuits, Hansastraße 32, 8068 Munich, Germany
  - name: Bernd Bischl \orcidlink{0000-0001-6002-6980}
    address: Department of Statistics, Statistical Learning and Data Science, LMU Munich, Ludwigstraße 33, 80539 Munich, Germany
